On The Impact of Atoms of Confusion in JavaScript Code

### 2022-07-22 4_Result.tex
The results section now has the two studies and the text is (mostly) consistent with the existence of these two studies.

Overall, this study had 70 participants. Out of these, 67 have received university-level training in programming, 4 hold a PhD degree, 7 hold a master's degree, and 11 hold a bachelor's degree. 
The median programming experience of the participants is four years (mean 6.5 years) and the median experience with JavaScript programming is one year (mean 2.5 years). 
% General programming: median: 48, 1st quartile: 22,5, 3rd quartile: 91,5
% JavaScript programming: median: 12, 1st quartile: 4, 3rd: 24

@@

The ``McNemar test'' column of Table~\ref{tab:repeated:misunderstanding} indicates the p-values for the tests. These p-values are compared against an alpha of 0.0021, after applying Bonferroni correction (0.05/24). One of the atom candidates, Constant Variables, is omitted from the table because, due to the very low number of mistakes, it is not possible to perform the McNemar test. The table shows that eight of the 24 analyzed atom candidates can be considered atoms of confusion based on the results of our study, Object Destructuring, Type Conversion, Change of Literal Encoding, Comma Operator, Indentation No Braces, Assignment as Value, Pre-Increment, and Ommitted Curly Braces. Among these eight, only Object Destructuring is JavaScript-specific. The other seven atoms have been previously reported for the C language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and also for Java~\cite{Langhout:2021:ACJ} (with the exception of Comma Operator). For some candidates that have been previously identified as atoms, there was not a statistically significant difference. This is the case for Repurposed Variables, Logic as Control Flow, Implicit Predicate, and Conditional Operator.

@@

We employ the non-parametric Mann-Whitney U test, also known as Wilcoxon's rank-sum test, to verify the aforementioned null hypothesis, i.e., to check whether the times for correct and incorrect answers can be considered identical. That test produces a p-value of \textbf{0.00000046}, which shows that the difference it statistically significant and we can reject the null hypothesis. To gauge the magnitude of that difference we employ Cliff's Delta as a measure of effect size. This produces a result of \textbf{0.1027}, which suggests that, although participants tend to provide correct predictions more quickly, they do that only slightly so.

@@

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{time} (how long to provide a correct answer).
We received full answers to our survey from 140 participants (a total of 70 replicas). All participants had taken at least some university course or hold a bachelor degree or equivalent, meaning the participants have had some level of formal education in programming. In addition, 21 participants hold a master's degree and three a doctorate degree. 
Considering the programming experience of our respondents, 19\% have more than ten years of programming experience, 37\% have between four and ten years of experience, 37\% have between one and four years of experience, and 7\% have less than one year of programming experience.  
Accordingly, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experienced developers.

\subsection{Misunderstanding Rate Analysis}
\castor{We need to be uniform about terminology. Are we going with ``misunderstanding rate analysis''? The problem is that it is not clear to me which rate is being referred to.}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten code snippets, from which five were in their confusing versions, whilst the other five contained clean versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{time}. 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

@@

We measure the effect size of the clean version of the code snippets into the answers' correctness using the \emph{Odds Ratio} (OR). The results are reported in the ``Odds Ratio'' column of Table~\ref{tab:hypothesis-testing}. In the table, we also report the confidence interval (CI) for the OR in the ``CI'' column. Although many of the intervals are wide, for six of the atom candidates the lower bound of the confidence interval is greater than or equal to 1. This indicates that, at a 95\% confidence level, a developer is likely to commit less mistakes when using the clean versions. 
%Considering only the atoms for which there was a significant difference in correctness for confusing and clean versions and u
Using the thresholds established by Chen and colleagues~\cite{Chen:2010:HBB} (OR = 1.68 small, 3.47 medium, and 6.71 large), for four of the atoms, Comma Operator, Automatic Semicolon Insertion, Assignment as Value, and Implicit Predicate, effect size can be considered large. For Implicit Predicate, it is medium. 
%We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. 
For instance, when comparing clean and confusing code snippets pertaining to the Comma Operator atom candidate, we observed an \emph{Odds Ratio} of \num{19.02}. This means that the odds of a correct answer are \num{19.02} times higher when interpreting the clean version---in comparison with the corresponding confusing version of the code snippet. Furthermore, with a 95\% confidence level, the odds  ratio is between 6.6 and 68.22, i.e., although the error margin is wide, it is strongly in favor of the clean version. If there is a significant likelihood of a developer committing a mistake when analyzing a clean version, the lower bound of the CI should be a number between 0 and 1 (since the OR is a ratio). This is the case for the four atom candidates in the lower part of the table. In particular, in the last row (Arithmetic as Logic), the OR between 0 and 1 indicates that a participant was actually more likely to misunderstand the clean version.

Finally, we also use a \emph{Binomial Generalized Logistic Regression} analysis to investigate if either \emph{participant education} or \emph{participant experience} impact correctness. The findings suggest that \emph{participant experience} impacts on the results related to correctness (Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers to all \emph{experience groups}, this effect is not uniform. For instance, novice developers (under one year of experience) provide a higher number of wrong answers for the confusing version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers even when evaluating the confusing version of the code snippets. It is also important to note that, independently of the \emph{experience group}, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code. We replicate the \emph{Pearson's Chi-squared test} for each experience group and find that the statistical difference is less significant for those developers with more than ten years of experience. Differently from \emph{participant experience}, the factor \emph{participant education} does not significantly change the correctness of the answers.

@@

Comparing to previous research, three 
atoms of confusion that Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} confirmed
for \clang and \cpplang do not lead to a statistically significant impact
on correctness in our study: Logic as Control Flow,
Conditional Operator, and Pre-Increment. Our results
support the Gopstein et al. findings for the remaining
atoms. The work of Langhout and Aniche~\cite{Langhout:2021:ACJ} investigates six atom candidates for Java that we also explore here for JavaScript. Among these atom
candidates, we achieve similar conclusions to their
study for four atom candidates: Post Increment,
Conditional Operator, Arithmetic as Logic, and
Omitted Curly Braces---both studies confirmed only the former
as an atom of confusion. Our findings diverged from
the work of Langhout and Aniche for two atoms: Pre Increment and
Logic as Control Flow.

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants to give a correct answer about the expected outcomes of a code snippet, considering both confusing and clean versions. We do not consider cases where the participants made mistakes. Seven atom candidates required more time from participants to predict a correct response. For these seven atom candidates, developers take at least 5.90\% less time on average to find a correct answer when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, require less time for the participants to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, the time to give a correct answer increased  
29.06\% and 38.19\% for the clean versions---we did not confirm these
atoms as atoms of confusion in the previous section.

@@

\subsubsection*{Statistical analysis}
We use the non-parametric \emph{Mann-Whitney U test}, also known as Wilcoxon rank-sum test, to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of clean and confusing versions of a code snippet.
%, regardless of evaluating the confusing or clean version of the code.
The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for five atom candidates (Comma Operator, Implicit Predicate, Logic as Control Flow, Pre-Increment, and Arithmetic as Logic), after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. For the first three, the analysis suggests that the participants need more time to predict the outcome of the code snippet in the confusing code version. For the atom candidates Arithmetic as Logic and Pre-Increment, the participants take less time to predict the outcome of the code snippets in the confusing version. We also computed the effect size using Cliff's Delta statistic. In the table, negative effect sizes suggest that it took less time to correctly predict the output of clean versions of the snippets.  Considering the thresholds established by Romano et al.~\cite{Romano:2006:ASO} (0.147 $<$ $|$d$|$ $<$ 0.33 small, $|$d$|$ $<$ 0.474 medium, otherwise large), we found a large effect for the Comma Operator atom candidate; a medium effect size for Logic as Control Flow, and small effect sizes for Automatic Semicolon Insertion, Implicit Predicate, Arithmetic as Logic, Post-, and Pre-Increment.

@@

In this section we present the results of the interviews with the practitioners. 
We contrast the findings of the survey presented in Section~\ref{sec:survey-resuts} here with the opinion
of software developers about their preferences regarding the confusing
or clean versions of the code snippets we used in our experiment.

@@

%In this section, we present the results of the 
% interviews with the 15 practitioners who agreed to participate in the study. 
A total of 15 practitioners took part of the interviews.
We collected information regarding programming
experience, familiarity with JavaScript, and their opinion about the \na atom candidates we explored in our research. We first presented them pairs of clean and confusing code snippets and then asked them to discuss their preferences towards one version. We did not indicate in any way whether any version was assumed to be confusing or not. 
% ask the participants to discuss their preferences (i.e., code with or without atom).

@@

\subsubsection*{The Participants' perceptions of the atom candidates} Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Conditional Operator atom candidate the participants prefer the confusing version, instead of the clean one. Figure~\ref{code:ternary} shows the code snippets for the corresponding confusing and clean versions. For this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

The Pre-Increment atom candidate also caused such
divide in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability.

@@

\begin{mq}
  \emph{``This one is interesting, because I have written code that looks like the left-hand side [confusing version], and my colleagues complained that it was difficult to understand. Nowadays I prefer to write code using the version on the right-hand side [clean version]''}.
\end{mq}

For two of the atom candidates, the interviewees were unanimous in their preference for the clean version: Comma Operator and Omitted Curly Braces. Regarding the first one, we could often notice during the interviews that the \emph{\lhs} (with the atom of confusion) caused significant confusion among the participants. One remark about the \emph{Comma Operator} atom of confusion is listed below:

@@

Two other developers implicitly touched upon the callback pattern, mentioning that it can be difficult to understand \emph{asynchronous} programming in JavaScript.
%Since what is really happening at a lower level is that the JavaScript engine creates a callback stack that is separate from the main execution stack, and that callback functions are only executed when the main execution stack is empty, the concepts of asynchronous events and callbacks are inseparable in the language, and any abstractions for callback functions, such as promises and async/await syntax only hide the pattern.
We also found other idioms that are JavaScript atom candidates, including
\emph{property access} via array subscription (\lstinline[language=javascript]{V1['P1']} instead of \lstinline[language=javascript]{V1.P1}) and \emph{arrow functions} (see listings~\ref{arr1} and~\ref{arr2}).  As future work, we aim at investigating whether or not these atom candidates are more likely to introduce confusion in JavaScript code.

>>>>

This study had 70 participants. Out of these, 67 have received university-level training in programming, 4 hold a PhD degree, 7 hold a master's degree, and 11 hold a bachelor's degree. 
The median programming experience of the participants is four years (mean 6.5 years) and the median experience with JavaScript programming is one year (mean 2.5 years). 
% General programming: median: 48, 1st quartile: 22,5, 3rd quartile: 91,5
% JavaScript programming: median: 12, 1st quartile: 4, 3rd: 24

@@

The ``McNemar test'' column of Table~\ref{tab:repeated:misunderstanding} indicates the p-values for the tests. These p-values are compared against an alpha of 0.0021, after applying Bonferroni correction (0.05/24). One of the atom candidates, Constant Variables, is omitted from the table because, due to the very low number of mistakes, it is not possible to perform the test. The table shows that eight of the 24 analyzed atom candidates can be considered atoms of confusion based on the results of our study, Object Destructuring, Type Conversion, Change of Literal Encoding, Comma Operator, Indentation No Braces, Assignment as Value, Pre-Increment, and Ommitted Curly Braces. Among these eight, only Object Destructuring is JavaScript-specific. The other seven atoms have been previously reported for the C language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and also for Java~\cite{Langhout:2021:ACJ} (with the exception of Comma Operator). For some candidates that have been previously identified as atoms, there was not a statistically significant difference. This is the case for Repurposed Variables, Logic as Control Flow, Implicit Predicate, and Conditional Operator.

@@

We employ the non-parametric Mann-Whitney U test, also known as Wilcoxon's rank-sum test, to verify the aforementioned null hypothesis, i.e., to check whether the times for correct and incorrect answers can be considered identical. That test produces a p-value of \textbf{0.00000046}, which shows that the difference is statistically significant and we can reject the null hypothesis. To gauge the magnitude of that difference we employ Cliff's Delta as a measure of effect size. This produces a result of \textbf{0.1027}, which suggests that, although participants tend to provide correct predictions more quickly, they do that only slightly so.

@@

In the latin-square study, we estimate the impact of atoms considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{time} (how long to provide a correct answer). In particular, in the time analysis, differently from the repeated  measures study, we compare the time required by participants to submit a correct response when analyzing code snippets with and without atom candidates. This study is based on the responses of 140 participants (a total of 70 replicas). All participants had taken at least some university course or hold a bachelor degree or equivalent. In addition, 21 participants hold a master's degree and three a doctorate degree. Considering the programming experience of our respondents, 19\% have more than ten years of programming experience, 37\% have between four and ten years of experience, 37\% have between one and four years of experience, and 7\% have less than one year of programming experience.  
Accordingly, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experienced developers.

\subsection{Misunderstanding Rate Analysis}
\castor{We need to be uniform about terminology. Are we going with ``misunderstanding rate analysis''? The problem is that it is not clear to me to which rate this refers.}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten code snippets, from which five were in their confusing versions, whilst the other five contained clean versions of the code snippets (i.e., without the atom candidates). As in the repeated measures study, the participants should provide the expected outcomes of the code snippets. Differently from that study, in this one each participant only predicts the outcome of one version of each code snippet, either clean or obfuscated. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{time}. 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

@@

We measure the effect size of the clean version of the code snippets into the answers' correctness using the \emph{Odds Ratio} (OR). The results are reported in the ``Odds Ratio'' column of Table~\ref{tab:hypothesis-testing}. In the table, we also report the confidence interval (CI) for the OR in the ``CI'' column. Although many of the intervals are wide, for six of the atom candidates the lower bound of the confidence interval is greater than or equal to 1. This indicates that, at a 95\% confidence level, a developer is likely to commit less mistakes when using the clean versions. 
%Considering only the atoms for which there was a significant difference in correctness for confusing and clean versions and u
%Using the thresholds established by Chen and colleagues~\cite{Chen:2010:HBB} (OR = 1.68 small, 3.47 medium, and 6.71 large), 
For four of the atoms, Comma Operator, Automatic Semicolon Insertion, Assignment as Value, and Implicit Predicate, effect size can be considered large. For Implicit Predicate, it is medium. 
%We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. 
For instance, when comparing clean and confusing code snippets pertaining to the Comma Operator atom candidate, we observed an \emph{Odds Ratio} of \num{19.02}. This means that the odds of a correct answer are \num{19.02} times higher when interpreting the clean version---in comparison with the corresponding confusing version of the code snippet. Furthermore, with a 95\% confidence level, the odds  ratio is between 6.6 and 68.22, i.e., although the error margin is wide, it is strongly in favor of the clean version. If there is a significant likelihood of a developer committing a mistake when analyzing a clean version, the lower bound of the CI should be a number between 0 and 1 (since the OR is a ratio). This is the case for the four atom candidates in the lower part of the table. 
%In particular, in the last row (Arithmetic as Logic), the OR between 0 and 1 indicates that a participant was actually more likely to misunderstand the clean version.

Finally, we also use a \emph{Binomial Generalized Logistic Regression} analysis to investigate if either \emph{participant education} or \emph{participant experience} impact correctness. The findings suggest that \emph{participant experience} impacts on the results related to correctness (Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers for all \emph{experience groups}, this effect is not uniform. For instance, novice developers (under one year of experience) provide a higher number of wrong answers for the confusing version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers even when evaluating the confusing version of the code snippets. It is also important to note that, independently of the \emph{experience group}, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code. We replicate the \emph{Pearson's Chi-squared test} for each experience group and find that the statistical difference is less significant for those developers with more than ten years of experience. Differently from \emph{participant experience}, the factor \emph{participant education} does not significantly change the correctness of the answers.

@@

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants to give a correct answer about the expected outcomes of a code snippet, considering both confusing and clean versions. We do not consider cases where the participants made mistakes. Seven atom candidates required more time from participants to predict a correct response. For these seven atom candidates, developers take at least 5.90\% less time on average to find a correct answer when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, require less time for the participants to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, the time to give a correct answer increased  
29.06\% and 38.19\% for the clean versions---we did not confirm these
atom candidates as atoms of confusion in the previous section.

@@

\subsubsection*{Statistical analysis}
We use the non-parametric \emph{Mann-Whitney U test} to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of clean and confusing versions of a code snippet.
%, regardless of evaluating the confusing or clean version of the code.
The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for five atom candidates (Comma Operator, Implicit Predicate, Logic as Control Flow, Pre-Increment, and Arithmetic as Logic), after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. For the first three, the analysis suggests that the participants need more time to predict the outcome of the code snippet in the confusing code version. For the atom candidates Arithmetic as Logic and Pre-Increment, the participants take less time to predict the outcome of the code snippets in the confusing version. We also computed the effect size using Cliff's Delta statistic. In the table, negative effect sizes suggest that it took less time to correctly predict the output of clean versions of the snippets.  Considering the thresholds established by Romano et al.~\cite{Romano:2006:ASO} (0.147 $<$ $|$d$|$ $<$ 0.33 small, $|$d$|$ $<$ 0.474 medium, otherwise large), we found a large effect for the Comma Operator atom candidate; a medium effect size for Logic as Control Flow, and small effect sizes for Automatic Semicolon Insertion, Implicit Predicate, Arithmetic as Logic, Post-, and Pre-Increment.

@@

In this section we present the results of the interviews with the practitioners. We contrast the findings presented in Section~\ref{sec:survey-resuts} with the opinion of software developers about their preferences regarding the confusing or clean versions of the code snippets we used in our experiment. For the interview study, we only considered atoms that were analyzed in both the repeated measures (Section~\ref{sec:repeated}) and the latin square (Section~\ref{sec:latin}) studies.

@@

%In this section, we present the results of the 
% interviews with the 15 practitioners who agreed to participate in the study. 
A total of 15 practitioners took part of the interviews.
We collected information regarding programming
experience, familiarity with JavaScript, and their opinion about the \na atom candidates we explored in the studies of the previous sections. We first presented them pairs of clean and confusing code snippets and then asked them to discuss their preferences towards one version. We did not indicate in any way whether any version was assumed to be confusing or not. 
% ask the participants to discuss their preferences (i.e., code with or without atom).

@@

\subsubsection*{The Participants' perceptions of the atom candidates}

Supporting the results of the studies of Sections~\ref{sec:repeated} and~\ref{sec:latin}, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Conditional Operator atom candidate the participants prefer the confusing version, instead of the clean one. Figure~\ref{code:ternary} shows the code snippets for the corresponding confusing and clean versions. For this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

The Pre-Increment atom candidate also caused such
divide in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability. In the repeated measures study, we found a significant difference in favor of the clean version, with a large effect size in its favor. In the latin square study, no difference could be observed in terms of correctness. However, there was a significant difference in terms of the time required predict the output correctly in favor of the obfuscated version. This highlights how factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}.
\castor{Should the last sentence above be in the discussion?}

@@

\begin{mq}
  \emph{``This one is interesting, because I have written code that looks like the left-hand side [confusing version], and my colleagues complained that it was difficult to understand. Nowadays I prefer to write code using the version on the right-hand side [clean version]''}.
\end{mq}
\noindent
None of the two studies found a significant difference in correctness between clean and obfuscated versions of snippets related to this atom candidate. However, in the latin square study the participants analyzing clean versions of the snippets required significantly less time.

For two of the atom candidates, the interviewees were unanimous in their preference for the clean version: Comma Operator and Omitted Curly Braces. Not coincidentally, in both studies there were significant differences in correctness in favor of the clean versions for both atoms. Regarding the first one, we could often notice during the interviews that the \emph{\lhs} (with the atom of confusion) caused significant confusion among the participants. One remark about the \emph{Comma Operator} atom of confusion is listed below:

@@

Two other developers implicitly touched upon the callback pattern, mentioning that it can be difficult to understand \emph{asynchronous} programming in JavaScript.
%Since what is really happening at a lower level is that the JavaScript engine creates a callback stack that is separate from the main execution stack, and that callback functions are only executed when the main execution stack is empty, the concepts of asynchronous events and callbacks are inseparable in the language, and any abstractions for callback functions, such as promises and async/await syntax only hide the pattern.
We also found other idioms that are JavaScript atom candidates, including
\emph{property access} via array subscription (\lstinline[language=javascript]{V1['P1']} instead of \lstinline[language=javascript]{V1.P1}) and \emph{arrow functions} (see listings~\ref{arr1} and~\ref{arr2}). The former was investigated in the repeated measures study but we did not find a significant difference between clean and obfuscated versions. As future work, we aim at investigating whether or not these atom candidates are more likely to introduce confusion in JavaScript code.

### 2022-07-22 discussion.tex
The results section now has the two studies and the text is (mostly) consistent with the existence of these two studies.

>>>>

% From the paper. I think it makes more sense to discuss this in the context of teh two studies. 
Comparing the results of the latin square study to previous research, three 
atoms of confusion that Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} confirmed
for \clang and \cpplang do not lead to a statistically significant impact
on correctness in our study: Logic as Control Flow,
Conditional Operator, and Pre-Increment. Our results
support the Gopstein et al. findings for the remaining
atoms. The work of Langhout and Aniche~\cite{Langhout:2021:ACJ} investigates six atom candidates for Java that we also explore here for JavaScript. Among these atom
candidates, we achieve similar conclusions to their
study for four atom candidates: Post Increment,
Conditional Operator, Arithmetic as Logic, and
Omitted Curly Braces---both studies confirmed only the former
as an atom of confusion. Our findings diverged from
the work of Langhout and Aniche for two atoms: Pre Increment and
Logic as Control Flow.
